---
title: "Penguins Random Forest Analysis"
author: "Alex Knowlton"
date: "6/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## my_rf_cv
`my_rf_cv` is a function that takes in a parameter of the number of folds to
use in cross-validation. It then attempts to predict the body mass of penguins
from the bill length, bill depth, and flipper length.

We can examine the effect of the cv parameter thus:
```{r}
library(ggplot2)
source("../Code/my_rf_cv.R")
k <- c(2, 5, 10)
result <- matrix(nrow = 90, ncol = 2)
colnames(result) <- c("n_folds", "cv_error")
for (i in 1:3) {
  for (j in 1:30) {
    result[(30) * (i - 1) + j, 1] <- k[i]
    result[(30) * (i - 1) + j, 2] <- my_rf_cv(k[i])
  }
}

result <- as.data.frame(result)
write.csv(result, "../Output/Results/cv_errors.csv")
fig <- ggplot(result, aes(x=n_folds, y=cv_error, 
                   group = n_folds)) + geom_boxplot() + labs(title = 
                          "Random Forest with 5-fold Cross validation",
                          x = "Number of folds", y = "Mean Squared CV Error")
ggsave("../Output/Figures/rf_boxplot.png")
fig
```

``` {r}
result_stats <- matrix(nrow = 3, ncol = 2)
colnames(result_stats) <- c("mean", "standard deviation")
rownames(result_stats) <- c("k = 2", "k = 5", "k = 10")
for (i in 1:3) {
  results_of_specific_k <- result[result$n_folds == k[i], 2]
  result_stats[i, 1] <- mean(results_of_specific_k)
  result_stats[i, 2] <- sd(results_of_specific_k)
}
result_stats <- (as.table(result_stats))
saveRDS(result_stats, "../Output/Results/rf_summary_stats.rds")
library(kableExtra)
kable_styling(kable(result_stats))
```

It's clear that, as the number of folds increases, both the mean squared error
and the standard deviation of the squared error decrease. This makes sense,
since as there are more folds, the model has more training data to work with,
and can get a better grasp on the data itself. Therefore, its predictions
would be better. There are also fewer predictions, so the mean squared error
should be smaller with a smaller number of people as well.
